### 2015-01-19 src/introduction.Rnw
update

% thus
% introduced behave in a fashion similar to real faults, with respect to
% the difficulty of detection.

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
%Recent work suggests that using statement deletion alone can
%be an effective approach~\cite{untch2009onreduced}.

@@

This paper studies different mutant selection strategies on large number of
Java programs using a popular bytecode-based mutation PIT.
We sampled $312$ opensource Java project between $50$ to $100K$ non-comment
lines of code (excluding test cases) from Github and Apache Foundation. This
set of projects include many of popular Java projects that are regualry used in
literature (such as Apache Common Lang, Common Math and Joda Time). For the
mutation analysis of this study, we choose PIT, a fast and easy to use mutation
analysis tool for Java, which has been used by researchers in the
past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range of
operators.
% Amin: Total lines of code, total number of mutants

For this study, we experimented four classic mutation selection techniques: Constrained \cite{wong1995reducing}, E-       Selective \cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and N-Selection
\cite{offutt1993experimental}, along with two sampling approaches: element based \cite{zhang2013ase} and operator based   sampling \cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no statistically significant benefit for mutation selection techniques. Moreover, in cases with statistically significant benefit, the gain is
so low that is essentially negligible.

\begin{comment}
We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
$312$ Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.
\end{comment}

% For a mutation selection strategy to be considered effective, especially during
% the development, it should be able to expose as many defect-like behaviors as
% possible.

% Alex: added
Given a set of mutants and a universe of test cases, we can approximate the
minimal set of test cases required to kill those mutants.\footnote{We only
approximate this, with greedy methods, due to the high cost of computing a
perfect minimal set, as established in the test case selection literature
\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that
require as many test cases as possible, if we assume that the original set
of test cases is populated with useful, non-redundant test cases.  While
the suites of many open source programs are far from adequate, they should
satisfy that requirement:  each test was almost always added by considerable
manual labor, and was at least believed to be useful.  Therefore, any tests
omitted likely indicate a potential to miss faults.  A good mutation selection
strategy, therefore, should 1) be as close to the original set of mutants
as possible, in terms of the test cases it requires in a minimal suite and
2) require more test cases than a randomly selected set of mutants of the
same size.

@@

% Alex: rm
% Consider any test in a test suite. It is written with the intent of
% checking for the absence of some (faulty) behavior. From the perspective of a
% a tester, the best testsuite is one that checks for the absence
% of the largest number of faulty behaviors. If tests were equivalent in the
% amount of behaviors that they verify, then the best testsuite would be one that
% encouraged adding the largest number of non-redundant test cases. However,
% it is possible that different tests are not equivalent in the number of
% behaviors that they check. We can approximate this to some extent by
% including the number of assert statements within each test~\footnote{We
% approximate the effect of exception-only test cases by starting the assert
% count from $1$ rather than $0$}.

>>>>

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to
generate mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.

@@

This paper studies different mutant selection strategies on large number
of Java programs using a popular bytecode-based mutation PIT.  We sampled
$312$ opensource Java project between $50$ to $100K$ non-comment lines of
code (excluding test cases) from Github and Apache Foundation. This set
of projects include many of popular Java projects that are regualry used
in literature (such as Apache Common Lang, Common Math and Joda Time). For
the mutation analysis of this study, we choose PIT, a fast and easy to use
mutation analysis tool for Java, which has been used by researchers in the
past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range
of operators.

For this study, we experimented four classic mutation selection
techniques: Constrained \cite{wong1995reducing}, E-Selective
\cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and
N-Selection \cite{offutt1993experimental}, along with two sampling
approaches: element based \cite{zhang2013ase} and operator based   sampling
\cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no
statistically significant benefit for mutation selection techniques. Moreover,
in cases with statistically significant benefit, the gain is so low that is
essentially negligible.

Given a set of mutants and a universe of test cases, we can approximate the
minimal set of test cases required to kill those mutants.\footnote{We only
approximate this, with greedy methods, due to the high cost of computing a
perfect minimal set, as established in the test case selection literature
\cite{yoo2012regression}.}  Ideally, we would like a set of mutants that
require as many test cases as possible, if we assume that the original
set of test cases is populated with useful, non-redundant test cases.
While the suites of many open source programs are far from adequate,
they should satisfy that requirement:  each test was almost always added
by considerable manual labor, and was at least believed to be useful.
Therefore, any tests omitted likely indicate a potential to miss faults.
A good mutation selection strategy, therefore, should 1) be as close to the
original set of mutants as possible, in terms of the test cases it requires
in a minimal suite and 2) require more test cases than a randomly selected
set of mutants of the same size.

@@
